Nic Steyn

### 2025-02-11 site/papers.qmd
minor updates

# Pre-prints

@@

@@

>>>>

# Preprints

@@

**Steyn, N.**, Unwin, H. J. T., Ponmattam, J., et al. Regional and national estimates of children affected by all-cause and COVID-19-associated orphanhood and caregiver death in Brazil, by age and family circumstance. *medRxiv preprint*. [https://doi.org/10.1101/2025.01.31.25321479](https://doi.org/10.1101/2025.01.31.25321479)

@@

# Awards

[**Prime Minister's Science Prize**](https://pmscienceprizes.org.nz). 2020.
Awarded for a "transformative scientific discovery or achievement" with a significant impact on New Zealand. This was awarded for our work on modelling during the COVID-19 pandemic in New Zealand.
